What is disputed on the web?

### 2010-01-26 papers/wicow_claimfinder/claimfinder.tex
Started work on WICOW paper. Added files that should have been committed earlier. Cleaned up .gitignore.

@@

\title{Highlighting Disputed Claims on the Web}

@@

\author{
	Author list to be determined
}

\author{
\alignauthor Rob Ennals\\
       \affaddr{Intel Labs Berkeley}\\
       \affaddr{2150 Shattuck Ave}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{robert.ennals@intel.com}
\alignauthor Beth Trushkowsky\\
       \affaddr{Computer Science Division}\\
       \affaddr{University of California at Berkeley}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{trush@cs.berkeley.edu}
\alignauthor John Mark Agosta\\
       \affaddr{Intel Labs Santa Clara}\\
       \affaddr{2200 Mission College Blvd}\\
       \affaddr{Santa Clara, CA, USA}\\
       \email{john.m.agosta@intel.com}
}

@@

\additionalauthors{Tye Rattenbury and Tad Hirsch, Intel Research Principles and Practices,\texttt{[tye.rattenbury,tad.hirsch]@intel.com}}

@@

\abstract

We describe Dispute Finder, a browser extension that alerts a user when information they read online is disputed by a source that they might trust. Dispute Finder examines the text on the page that the user is browsing and highlights any phrases that resemble known disputed claims. If a user clicks on a highlighted phrase then Dispute Finder shows them a list of articles that support other points of view.

Dispute Finder builds a database of known disputed claims by crawling web sites that already maintain lists of disputed claims, and by allowing users to enter claims that they believe are disputed. Dispute Finder identifies snippets that make known disputed claims by running a simple textual entailment algorithm inside the browser extension, referring to a cached local copy of the claim database.

In this paper, we explain the design of Dispute Finder, and the trade-offs between the various design decisions that we explored.

\category{H.4.m}{Information Systems}{Miscellaneous}
\category{H.4.2}{Information Systems}{Decision Support}
\category{H.5.2}{User Interfaces}{Graphical User Interfaces}

@@

\todo{update screenshots}
\todo{should this be spun as about news, or information in general}
\todo{need to talk more about what we know about people}

% The last few years have seen the rapid decline of printed newspapers and rapid rise of the web as a source of news~\cite{pew-news?}.

The web contains a huge amount of information, but some of this information is factually incorrect and some sites present only one side of a contentious issue~\cite{Herman2002}. If a user is to gain a broad understanding of a topic then they will need to either spend time searching for alternative points of view, or restrict themselves to sources that they believe they can trust to provide accurate and balanced information. Even when a user spends time investigating every claim that they think might be disputed, they can still be misled by information that they had not realized was disputed.

In recent years, we have seen the emergence of a new class of tools that help users recognize and make sense of disputed information on the web. In this paper, we describe Dispute Finder, a tool that alerts a user when a web page they are reading appears to be making a claim that is disputed by a source that they might trust.

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8.5cm]{pictures/highlight_abortion.png}
	\caption{Dispute Finder highlights text snippets that make disputed claims.}
	\label{highlight}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=7cm]{pictures/popup_abortion_shadow.png}
	\caption{Click on a highlighted snippet to see a popup interface with articles arguing for and against the claim.}
	\label{claimview}
	\end{center}
\end{figure}
\todo{Popup interface should contain a ``don't mark this'' button}

\todo{More screenshots/graphs/visual information}

\todo{word this better}\todo{update all screenshots}

%In this paper we describe Dispute Finder, a tool that alerts a user when information they read online is disputed by a source that they might trust. Our hope is that Dispute Finder will make it easier for a user to gain a broad view of a topic that they are interested in by exposing them to different points of view.

A user can install Dispute Finder as an extension to the Firefox\footnote{http://www.mozilla.org/firefox} web browser. When installed Dispute Finder will highlight snippets of text that make disputed claims (Figure~\ref{highlight}). 
If a user clicks on a highlighted snippet, Dispute Finder will show articles that put forward alternative points of view,  each of which is from a source we believe the user might trust (Figure~\ref{claimview}).

Dispute Finder consists of a server-side database and a Firefox browser extension. The database contains a set of known disputed claims that frequently appear on the web. A disputed claim is a statement about the world that some people disagree with. For example ``global warming is a hoax'', ``gun control will reduce crime'', ``Eskimos have many words for snow'', or ``margarine is healthier than butter''. A claim can be stated in many ways. For example ``margarine is healthier than butter'' and ``butter is worse for you than margarine'' are {\it paraphrases} of the same claim. For each claim, the database contains links to articles on the web that support or oppose it, and hints about how to recognize that disputed claim on the web (Figure~\ref{snippet_claim_article}).

The browser extension maintains its own local copy of the database, and scans the text on the current page for text snippets that appear to {\it entail} a claim. A snippet is a continuous region of text on a web page. A snippet is considered to {\it entail} a claim if a typical user reading that snippet would reasonably conclude that the author of the page believed the claim was true. For example ``the English have as many words for rain as the Eskimos have for snow'' {\it entails} ``Eskimos have many words for snow'', even though this claim is never stated explicitly.

\todo{Should we mention the API? Cut from this version as tangential}

In this paper, we describe the design of Dispute Finder, the constituent problems that must be solved to make a tool like Dispute Finder work well, the trade-offs we encountered between different design choices, and our experiences testing Dispute Finder with users.

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8.5cm]{pictures/snippet_claim_article_fancy3.png}
	\caption{Snippets entail claims. Claims are entailed or contradicted by articles.}
	\label{snippet_claim_article}
	\end{center}
\end{figure}

\subsection{Personas}

If users are going to adopt Dispute Finder, it is important that it solves a real need. We used interviews to construct two personas which model the two ways that we expect a user to use Dispute Finder.

{\it Skeptical Readers} want to know when something they read is disputed by a source that they might trust. They are skeptical about the accuracy of the information that they read and often check multiple sources to get different opinions on a topic. A user will typically behave like a skeptical reader for some topics and not others. For example a user may be skeptical when reading about topics that affect them (e.g. health, things important to their job, or things they are expected to be knowledgeable about), but disengaged when reading about topics that do not affect them (e.g. entertainment).

{\it Activists} care strongly about particular issues and are prepared to spend some time informing others that something that they disagree with is disputed. They are the same kinds of people who join protest groups, write blogs, email news stories, or argue about topics online. They are motivated by a desire to influence others and to gain status by being seen to do so. A user is likely to be an activist on some issues, but not on others. An activist will often also be a skeptical reader.

Many users fall into neither of these two personas. If a user does not regularly read information online that they feel they need to need to understand well, or restricts their reading to sources that they believe they can trust, then they are unlikely to be interested in a tool like Dispute Finder.

@@

There is ample evidence that at least some people are skeptical about the information they read and would like to know about alternative points of view that are supported by sources that they trust. This has lead to a growing set of tools that aim to help users deal with disputed and biased information.

According to Pew Research~\cite{PewResearch2008}, a substantial proportion of people regularly get information from sources that they do not fully trust. Their 2008 survey found that 33\% of Democrats regularly watch Fox News, and yet only 19\% believe all or most of what Fox News says. Similarly, 51\% of Democrats regularly watch CNN, and yet only 35\% believe all or most of what CNN says. While these figures are for TV News, rather than the web, Pew report that 48\% of web users people regularly follow search links to unfamiliar sources, and that users view online sources such as blogs with more skepticism that their print, broadcast, and cable counterparts.

These findings were backed up by our interviews (Section~\ref{sec:interviews}). Several participants told us that they regularly get information from sources that they do not entirely trust. A user might read information from an untrusted source because the source is interesting, entertaining, linked to from somewhere else, or it came up in a search. For example they might read Michael Moore because he is entertaining, while having low opinions of his credibility, or they might read articles mailed to them by friends.

\todo{Talk about people reading from a wide range of sources.}

There is also evidence that a significant group of people are interested in checking information they read on the web. Several popular web sites are designed primarily to help users check information they read elsewhere. For example Snopes.com contains information about urban myths such as ``eskimos have many words for snow'' and Factcheck.org and Politifact.com investigate claims made by American political figures. According to Quantcast.com, Snopes has around five million unique visitors per month.

To check these assumptions, we circulated a survey among members of a local debate club, who we anticipated would be a good match for our Skeptical Reader and Activist personals. Of the 23 people who responded, 91\% said that they sometimes or often check information they read on a trusted site (64\% often, 27\% sometimes) and 91\% said that they sometimes or often check information by searching for other web pages about the same topic (74\% often, 17\% sometimes).

\todo{Talk about our survey}

Fact checking web sites and search engines work well when you know something is disputed, but are of little use if you did not realize that what you were reading was disputed. The primary aim of Dispute Finder is to let you know when something you are reading is disputed.

Many other tools highlight disputed information on web pages. ReframeIt.com, ShiftSpace.org and SpinSpotter.com allow a user to manually annotate a web site that they disagree with, overlaying their own opinions on top of existing content. Videolyzer~\cite{Diakopoulos2008} allows users to comment on disputed claims in video clips. There are many other web annotation tools, including Google SideWiki, Annotea~\cite{Koivunen2001} and ScreenCrayons~\cite{Olsen2004}, each of which presents a different combination of features, and most of which could be used to annotate disputed content.

There are two key differences between Dispute Finder and these annotation tools: First, rather than allowing a user to express their own opinions about a topic, Dispute Finder instead requires a user who wants to promote a particular opinion to do so by linking to an article from a trusted source that argues for that opinion. Our interviews (Section~\ref{sec:interviews}) lead us to believe that most users would rather know that a trusted source disagrees with what is being written than that an unknown user disagrees.

The second key difference between prior annotation tools and Dispute Finder is that prior annotation tools allow a user to annotate {\it text on a particular page} while Dispute Finder attempts to allow a user to annotate a {\it general claim, everywhere it appears on the web, however it is worded}. If a user of an annotation tool adds an annotation to a page then their annotation will only appear on that page. If a user of Dispute Finder tells Dispute Finder to highlight a disputed claim, that claim will be highlighted on every web page on which Dispute Finder's algorithms determine that the claim appears. The closest annotation system to Dispute Finder in this respect is perhaps SparTag.us~\cite{Hong2009}, which uses an SHA hash to attach an annotation to an exact paragraph, irrespective of where it appears on the web; however a claim may be written in many different ways, and be part of many different paragraphs.

Several Sensemaking, Decision Support, and Argumentation tools allow a user to annotate a document with structured information that they may then share with other users. TRELLIS~\cite{Gil2002} helps a user annotate the rationale for their decisions and opinions by annotating source documents with the facts that they extracted from them, and connecting these facts into a decision graph. ClaimSpotter~\cite{Sereno2005,Sereno2004} applies a similar approach to scholarly papers, allowing a user to make up a paper with logical subject-verb-object triples describing important claims made in the document. Entity Workspace~\cite{Bier2006} uses entity extraction algorithms to allow an intelligence analyst to easily mark up a source document with facts extracted from it. Cohere~\cite{Shum2008} is a web based argumentation tool that allows people to connect {\it ideas} together using arbitrary verbs such as ``is an example of'', ``supports'', or ``challenges''. An idea can contain a link to a web page that contains that idea, and the Cohere Firefox Extension informs a user when the page that they are is the source for a known idea.

These tools allow a user to mark up the facts made by a single document, but do not provide facilities for a user to mark up large numbers of documents as being the same claim, or to automatically inform a user when other sources disagree with what they are reading.

There are also several tools that find pages write about the same topic with different slants, rather than looking at the specific claims a page makes. News Cube~\cite{Park2009} automatically finds articles that present different {\it aspects} of the same news story. The intention is that by reading several such aspects, the user will encounter several different ways of looking at the issue at hand, and will gained a broader perspective of the issue. 
Services such as Skewz.com and Newstrust.net allow users to rate news articles for bias. Skewz rates stories as being either liberal or conservative and encourages readers to read what the other side is thinking. Newstrust allows users to rate news articles for quality and objectivity.

On Wikipedia, WikiTrust~\cite{Adler2008a} highlights passages on Wikipedia that are statistically likely to be reverted, based on how recently they were written and the track-record of the author, Wiki Dashboard~\cite{Kittur2008} creates a visualization of the edit history of a Wikipedia article that lets a user see how contentious it is, and Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds cases where a Wikipedia edit has been made by someone with a conflict of interest. These tools have a similar aim to Dispute Finder, but are limited to Wikipedia.

More generally, Dispute Finder is an example of an Open Hypermedia system~\cite{Bouvin2000,Wiil1996}. Like other Open Hypermedia systems, Dispute Finder lays an additional link structure over an existing hypertext document. In the case of Dispute Finder, the links are from disputed claims to information about those claims.

Dispute Finder also has some similarity to tagging tools~\cite{Marlow2006,Golder2006}. Tagging tools allow users to collectively categorize information by associating it with a user-created set of tags. In the case of Dispute Finder, the tags are disputed claims, and the tagged entities are sentences that make those claims.

\todo{Improve the paraphraser UI so it shows users what pages are making the claim}
\todo{Improve the ``see examples on the web'' UI to it shows the pages that were found with the activists training work}
\todo{Provide a customized RSS reader and search engine that does dispute tracking. - future work?}
\todo{Should we explicitly list what we think are our key contributions?}

\section{Design}

Creating a tool to manage disputed information requires designers to address a number of challenges, including:

\begin{description}
\item[Developing a corpus of disputed claims:] To be useful, the set of known disputed claims needs to be both large and credible. If the database's coverage is too small then users will rarely see snippets highlighted. If the database is not credible then users will often see snippets highlighted for which there is no credible evidence for other points of view.

\item[Detecting these disputed claims on the web:] Given a particular web page, how do we determine which phrases on that page are making known disputed claims and should be highlighted? There is a trade-off between precision and recall. We do not want to highlight a snippet that is not making a disputed claim, but we do want to maximize the likelihood that we highlight a snippet that is making a disputed claim.

\item[Highlighting disputed claims for users:] If we are to alert a user when they read disputed information, we need to be able to tell what text they are reading, and we need a way to inform them that this information is disputed. Ideally, this method should apply to as much of the information the user reads as possible, and be easy for a user to adopt. We also want to avoid distracting the user unnecessarily, while also making sure that they notice disputed claims that they would care about.

\item[Providing tools that help users interpret disputed claims:] Once a user has learned that a claim is disputed, it is likely that they will want to see information that will help them decide whether they should believe the claim and what other sources they should read. We want to help a user understand both {\it who} holds other points of view and {\it why} other people hold different points of view.

\item[Determining Trustworthy Sources:] What sources should we consider ``trustworthy'' in the sense that their opinions are worth presenting to the user, and things that they disagree with should be highlighted as disputed. There is a trade-off between showing a user sources that they will trust, and showing them sources that will expose them to a new point of view.
\end{description}

These challenges are not unique to dispute finder; indeed they apply to any tool that informs a user about disputed information and helps users interpret this disputed information.

In the rest of this section, we discuss the various alternative solutions that we explored for each of these problems, and our experiences with the approaches that we implemented and tested.

\subsection{Developing a Corpus}
\label{sec:disputed}

Dispute Finder maintains a shared server-side database of known disputed claims. The browser extension highlights a text snippet if it believes that the snippet entails one of the claims in this database (Figure~\ref{snippet_claim_article}). Claims can either be added directly by users (Figure~\ref{add_claim}) or mined from web sites such as Snopes and Politifact that already maintain well curated databases of disputed claims,

This database should not contain contain everything that has ever been disputed by anyone. In some sense almost everything is disputed by someone on the web. There are enough people writing enough opinions that if we alerted users every time anything they read was disputed by anyone then Dispute Finder would be so distracting as to be worthless. Similarly, there is little point spending effort rebutting claims that nobody believes. For example there is reliable evidence opposing the claim that the moon is made of cheese, but few people believe this claim is true. What we want is a set of claims that are widely believed and for which there is credible evidence supporting other points of view.

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{pictures/add_claim_list.png}
	\caption{A user can use this interface to add a new disputed claim manually.}
	\label{add_claim}
	\end{center}
\end{figure}

Currently most of our claims are automatically mined from Snopes and Politifact. Both of these sites maintain well curated databases of disputed claims, together with information about them. Snopes has good coverage of urban myths, and Politifact has good coverage of claims made by American politicians. In the future we plan to crawl other sites that cover other kinds of disputed claims (e.g. medical claims) and to provide an API to allow any site to provide a well-structured feed that we can use. At the time of writing, Dispute Finder has imported 1,457 claims from Snopes and 595 claims from Politifact.

One weakness of the automatic import approach is that the claims found on these sites are often phrased differently to the way they commonly appear on the web. For example many of the claims on Politifact are exact quotes such as ``One-third of the health care dollar goes to no such thing as health care; it goes to the insurance companies''. In practice, it is often necessary for users to enter several simple paraphrases for a claim before it can be reliably detected.

Dispute Finder also provides users means to add their own disputed claims using the Dispute Finder web interface (Figure~\ref{add_claim}). The web interface is modeled after common issue-reporting software such as Uservoice.com and Bugzilla.org. It first encourages the user to search the existing database to see if their claim already exists, and then allows them to create a new claim. When the claim is first added it is marked with a warning, informing the user that the claim will not be highlighted for other users until they have added at least one opposing article. At the time of writing, users have added 557 claims, and 140 users have added at least one claim.

%The automatic import bootstraps Dispute Finder with a useful database of disputed claims without needing a large active user community, and the crowd-sourcing aspect allows users to clean up claims that were not phrased well when imported, and add claims that are not part of any of our input feeds.

An alternative approach would be to use Contradiction Detection~\cite{Ritter} to find frequently repeated statements that appear to contradict statements from trusted sources. Unfortunately at the time of writing, Contradiction Detection does not seem to be robust enough for us to use it for this purpose.

In future work, we hope to automatically find disputed claims on the web by looking for phrases like ``falsely claimed that X'' --- a similar techniques to that used by Hearst to find hyponyms~\cite{Hearst1992}, and then use context to help determine which phrases are likely to be making the same claim.

\todo{Say how many disputed claims}
\todo{talk about duplicates}
\todo{Actually import the Politifact data}

\subsection{Detecting Known Disputed Claims}

Dispute Finder highlights a snippet if it thinks it entails the truth of a known disputed claim. This is complicated by the fact that a claim can be phrased in many different ways, and a snippet does not need to explicitly state a claim in order to entail its truth. For example ``I prefer margarine to butter because it is healthier'' entails ``margarine is healthier than butter''. Our implementation maintains a local copy of our claim database inside the browser extension and runs a simple textual entailment algorithm inside the browser to look for sentences that appear to entail known disputed claims.

There is a trade-off between precision and recall. We want to maximize the likelihood that Dispute Finder will highlight a snippet if it is making a known disputed claim, while minimizing the likelihood that it will highlight a snippet that is not making a known disputed claim. We implemented and tested four different approaches that represent different points along this trade-off:

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/mark_disputed.png}
	\caption{Explicit page marking: select the snippet and click ``this is disputed'' on the context menu.}
	\label{mark_disputed}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=7cm]{pictures/training2.png}
	\caption{Bulk page marking and server-side classification: classifier guesses are shown below the choice buttons.}
	\label{training}
	\end{center}
\end{figure}

\begin{figure}[t]
	\begin{center}
	\includegraphics[width=8cm]{pictures/nlp_client_server2.png}
	\caption{Client-side entailment: the entailment algorithm runs on the client, using a claim database downloaded from the server.}
	\label{nlp_client_server}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{pictures/paraphrases.png}
	\caption{Users can enter paraphrases of a claim to help the entailment algorithm.}
	\label{paraphrases}
	\end{center}
\end{figure}

\label{sec:explicit_mark}
\begin{description}
\item[Explicit page marking:] The user explicitly marks a snippet on a page by selecting the snippet, and selecting ``mark as disputed'' from a context menu (Figure~\ref{mark_disputed}).

\item[Bulk page marking:] The user uses a search interface to rapidly gather many snippets that contain similar phrases, and then selects those that they would like to mark (Figure~\ref{training}). The server uses Yahoo BOSS\footnote{http://developer.yahoo.com/search/boss} to search the web for snippets that resemble a paraphrase entered by the user.

\item[Server-side classification:] The server uses the examples from the bulk page marking interface to train a classifier. We used a simple Bayesian classifier with n-grams as features. The classifier looks at the positive and negative examples given by the user and learns n-grams that should or should not be present in a snippet in order for it to make the claim.  Once the classifier has been trained, the server uses it to refine which other results from Yahoo BOSS should be marked (Figure~\ref{training}).

%We have only partially implemented this approach.
\todo{Should we say that we didn't completely finish this version?}

\todo{Has anyone done something like this before.}
\todo{We only partially implemented this approach}

\item[Client-side entailment:] The browser extension runs a simple textual entailment algorithm over all sentences on every web page the user browses, checking to see if any sentence on the page entails any claim in the database (Figure~\ref{nlp_client_server}). A user can enter additional paraphrases of a claim to help the entailment algorithm (Figure~\ref{paraphrases}). This is the implementation used by the released version of Dispute Finder.
\end{description}

Explicit page marking has the highest precision, but the poorest coverage. Since a user is looking at the page in its entirety, they can read the snippet in context and make a good judgment about whether the snippet is indeed making the claim. However the manual effort required per page makes it difficult for this approach to scale. We also found that it can also be hard to motivate a user to mark snippets if they think that it is unlikely that another user with the Dispute Finder extension will read exactly this page. This same problem has hindered the adoption of numerous web page annotation tools.

Bulk page marking trades off some precision for better coverage. When a user searches for a phrase, they can quickly find hundreds of snippets and mark them by clicking on them. Since they are reading the snippet out of context, they are more likely to mark a phrase incorrectly.

Server side classification trades off more precision for more coverage. The classifier can mark more pages than a user could ever mark manually, and can keep marking new pages as they appear, but it is inevitably less accurate than a human.

Client side entailment gets the most coverage. Since the classification algorithm is run inside the client, the client can highlight snippets on pages that the server has not examined. This is particularly important for news pages, which are frequently read only a few minutes after they are posted. Moreover, the client-side approach can highlight snippets on web pages that would not be accessible to the server, such as web-based email, and intranet sites.

A further advantage of the client-side approach is that it avoids the need for the client to give the server any information about what pages the user is browsing. The list of all URLs and snippets that make disputed claims is too large and updates too frequently for it to be practical for the client to store it locally, so the client instead asks the server for information about each URL the user browses, reducing user privacy. By contrast, the list of paraphrases is small enough and changes slowly enough that the client can maintain its own local copy of the database, removing the need for the client to tell the server what pages the user is browsing. As our database grows bigger, it will of course become more challenging to maintain a local copy in the browser extension.

\subsubsection{Textual Entailment}

Detecting entailment between texts is a semantic analysis problem. Our client side entailment method uses the standard Local Lexical Matching (LLM) algorithm~\cite{Jijkoun2006} that is a common baseline to which other algorithms are often compared~\cite{Braz}. Our implementation divides the page into sentences, strips out stop-words, does stemming, and then looks for sentences that contain the keywords contained in a paraphrase of a known claim. If the claim contains a negation word (e.g. not, never, can't) then so must the matching sentence. To improve performance, rather than always running the LLM algorithm on every sentence on every page the user browses, the client starts by quickly scanning the page for ``hot terms'' such as ``Global Warming'' that are known to appear in disputed claims. The hot terms are selected such that every claim contains at least one hot term. If a hot term is found, then the sentence that contained the hot term compared against all claims about that hot term.

LLM is far from being state of the art and many more sophisticated textual entailment algorithms exist. Modern approaches include treating the sentence as a logical formula and attempting a logical proof~\cite{Bayer2001,Bos2005}, parsing each phrase into a syntax tree and using syntax heuristics~\cite{Snow2006}, inferring inference rules that can transform one sentence into another while preserving meaning~\cite{Lin2001,Dinu2009,Bhagat2009}, and using Bayesian inference to infer whether one phrase looks like the kind of phrase that would have included each word in the other phrase~\cite{Glickman2005}. Tools such as AuContraire~\cite{Ritter} focus specifically on detecting contradictions. Several tools rely on an underlying information extraction tool such as TextRunner~\cite{Etzioni2008}.

While Dispute Finder would almost certainly improve its precision and recall if it used a more sophisticated algorithm, LLM has the advantage of being simple enough to run efficiently inside a user's web browser for every page they look at without causing a noticeable slowdown. We do however believe that there is scope to use more sophisticated algorithms, particularly as processor speeds improve.

\todo{Mention that we could add the +ve and -ve n-grams to the client code? Actually do this?}

\todo{Discuss how and why this is simpler than the server-side classification method}
\todo{Explain how we avoid downloading the entire database}

\todo{Should we have a version where the interface merely suggests n-grams that should be used by the classifier}
\todo{Can we present all these systems without giving detailed stats about how they compare?}
\todo{Add support for a user to enter 'anti-phrases' when a snippet is wrongly highlighted}
\todo{Add support for a user to enter a paraphrase that will match the snippet they are looking at}
\todo{Do a load more people in a final user-study round. Try to get it up to 8.}
\todo{Explain how our algorithm relates to existing NLP work - due to unusual domain}

Other authors have used similar algorithms to find repeated information on the web. Kolak and Schilit~\cite{Kolak2008} look for passages places where one book quotes another, qSign~\cite{Kim2009} looks for places where one blog has quoted another, and duplicate-detection is often used to clean up web searches~\cite{Theobald2008}. MemeTracker~\cite{Backstrom2009} looks for phrases shared by multiple news stories, accounting for minor variations, and uses this to track the way that news flows between traditional news sources and blogs.

The authors of MemeTracker observed that many ideas often flow around the web in the form of ``memes'' that are repeated on many web sites with relatively little variation. To the extent that this is true, it simplifies identifying snippets that repeat the idea. MemeTracker uses this to track the way an idea propagates across the web using a relatively simple algorithm. We have found that the precision and recall of our client-side textual entailment algorithm varies hugely depending on how meme-like a claim is. Some claims (particularly those derived from quotes) are widely repeated almost-verbatim, and can be detected relatively easily. However many other claims are rarely stated explicitly in a single sentence or with the same choice of words, making them much harder to detect with a simple algorithm.

\todo{Give an example of a good meme}

\todo{Talk about what dispute finder does, and how it differs - maybe by moving this into the main system section}
\todo{Cite plagarism detection}
\todo{Talk about how our algorithm looks for key terms used in disputed claims}
\todo{Talk about how our first pass NLP algo is rather like }

\subsection{Highlighting Disputed Claims}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{pictures/highlight_bar.png}
	\caption{Dispute Finder highlights text snippets that make disputed claims, and displays a notification bar to inform the user that they should look out for highlighted snippets.}
	\label{highlight_bar}
	\end{center}
\end{figure}

%Dispute Finder is designed to alert a user when information they read on a web page makes a claim that is disputed by a source they might trust. 
%
%
%Dispute Finder aims to inform users when information they read on the web makes claims that are disputed by sources that they might trust. We are particularly interested in informing users about claims that they hadn't thought about before, hadn't realized were disputed by sources they repect, or have not yet established a strong opinion on.

The Dispute Finder Firefox extension uses two mechanisms to inform a user when information on the page they are reading is disputed. It highlights any disputed snippets in red, and it displays a notification bar (Figure~\ref{highlight_bar}).

The notification bar alerts the user that they should look out for highlighted snippets. Highlights can be difficult to see if the page is using a background that is similar to our highlight color\footnote{We tried to choose a color that is easily distinguished from most background commonly used background colors.} particularly if the user is color blind. The notification bar also allows a user to step through the highlighted snippets on the page.

The highlights show a user {\it which snippets} Dispute Finder believes are making disputed claims. A user can see whether the highlights are in the text that they are reading and ignore disputed snippets in text that they are not interested in - such as user comments. The highlights also allow a user to see when Dispute Finder has incorrectly inferred that a phrase as making a disputed claims that it is not making. In such cases, the user is encouraged to help Dispute Finder improve its marking by clicking on the disputed claim and clicking on the ``report incorrect highlighting'' button from the popup interface.

Once a user is aware that a claim is disputed, there is little point telling them about the same disputed claim again in the future. We have not yet concluded whether it is better for Dispute Finder to automatically stop highlighting a claim once a user has viewed the claim, or whether it is better for a user to explicitly ask Dispute Finder to stop highlighting a claim. In our current implementation, a user can tell Dispute Finder to not highlight a claim again by setting the ``don't highlight this claim for me again'' checkbox in the popup interface (Figure~\ref{claimview}). Requiring a user to manually opt out of a claim requires more work from the user, but hiding already viewed claims can be confusing, since users do not normally expect viewing something to be a destructive operation. A compromise position is to highlight claims that have been seen before in a fainter color; similar to the way links are typically colored on web pages.

\todo{Try using a fainter color}

\todo{Text is wrong in the screenshot}

Dispute Finder also provides an API that allows other sites to determine whether their content makes disputed claims. For example, a search engine could inform a user if its results contained disputed claims, or an RSS feed reader could tell a user if a news story makes disputed claims.

\todo{Document API online}
\todo{Change the highlight color to yellow? Auto-adjust highlight color based on background color?}
\todo{Should we automatically adjust the highlight color, based on the background color of the page}
\todo{Discuss previous work on highlighting here, rather than in related work?}

\subsection{Helping Users Interpret Claims}

When a user clicks on a highlighted snippet, Dispute Finder displays a popup pane with information intended to help the user determine whether there are alternative points of view that they should take seriously, and whether there are articles on this topic that they should read. In our current implementation, the popup interface shows lists of articles that support or oppose the claim (Figure~\ref{article_list}). We also implemented and tested an interface that contained a user-editable argumentation graph; however we found that users had difficulty creating such graphs and were more interested in {\it who} disagreed with a claim than {\it why} people disagreed with it.

We could have omitted this claim-information feature and still had a useful system. Once a user sees that something is disputed, they could use an alternative service, such as a search engine, Wikipedia, Politifact or Snopes, to find further information about the claim. There are however several reasons why it makes sense for Dispute Finder to maintain information about a disputed claim:

\begin{description}
\item[Convenience:] A user may not have the patience to search for a good source of information about a claim. 
\item[Moderation:] We only want Dispute Finder to highlight a claim if we know that there is credible evidence for an alternative point of view. By storing the evidence for alternative points of view inside Dispute Finder, it becomes easier for a moderator user to evaluate whether a claim is sufficiently disputed that it belongs in the Dispute Finder database.
\item[Filtering:] Although we have not implemented this feature currently, we think it could be useful to build a model of what sources a user trusts and only highlight a disputed claim if a source that the user trusts argues against it.
\end{description}

We prototyped and tested two different ways of showing a user alternative points of view to the disputed claim they are looking at:

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/popup_abortion_shadow.png}
	\caption{Article List interface for a disputed claim}
	\label{article_list}
	\end{center}
\end{figure}

\begin{description}
\item[Argumentation graph:] When the user clicks on a snippet that makes a disputed claim, Dispute Finder shows them a simple user-editable argumentation graph. This graph is inspired by IBIS~\footnote{Issue Based Information System} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}. Each claim is linked to claims that represent alternative points of view, and claims that support that point of view. Each claim also has a list of articles that argue in favor of that claim (Figure\ref{popup_graph})

\item[Article lists:] Dispute Finder shows the user two lists of articles, one of which contains articles arguing in favor of the claim, and the other of which contains articles arguing against the claim (Figure~\ref{article_list}). For each article, the interface shows a summary sentence that captures the core argument used by the article. A user can add any web page as a supporting article by browsing to the page, selecting ``use as evidence'' from a context menu (Figure~\ref{add_article}) and then saying what claim it supports or opposes (Figure~\ref{article_choose}).
\end{description}

The argumentation graph makes it easier to see {\it why} a claim is disputed, while the article lists make it easier to see {\it who} supports or opposes the claim.

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/mark_evidence.png}
	\caption{To add an article, select some summary text, and click ``use as evidence'' from the context menu.}
	\label{add_article}
	\end{center}
\end{figure}

>>>>

% Mark up a point that we want to flesh out into more text
\newcommand{\x}[1]{{\color{blue} #1}\\}

@@

\title{What is disputed on the web?}

@@

\author{
\alignauthor Dan Byler\\
       \affaddr{School of Information}\\
       \affaddr{University of California at Berkeley}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{dan@ischool.berkeley.edu}
\alignauthor Rob Ennals\\
       \affaddr{Intel Labs Berkeley}\\
       \affaddr{2150 Shattuck Ave}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{robert.ennals@intel.com}
\alignauthor John Mark Agosta\\
       \affaddr{Intel Labs Santa Clara}\\
       \affaddr{2200 Mission College Blvd}\\
       \affaddr{Santa Clara, CA, USA}\\
       \email{john.m.agosta@intel.com}
}

@@

\additionalauthors{Barbara Rosario, Intel Labs Santa Clara, \\\texttt{[barbara.rosario@intel.com]}; Tye Rattenbury and Tad Hirsch, Intel Research Principles and Practices,\\\texttt{[tye.rattenbury,tad.hirsch]@intel.com}}

@@

\abstract
[Final author list is to be determined]

%\subsection{Categories and Subject Descriptors}
%\todo{Categories, terms, and keywords need updating}
\category{H.3.1}{INFORMATION STORAGE AND RETRIEVAL}{Content Analysis and Indexing}
\category{I.2.7}{ARTIFICIAL INTELLIGENCE}{Natural Language Processing}

@@

\x{Information credibility is important.}
\x{People are increasingly relying on the web for information.}
\x{People read a wider range of sources that before, many of which they do not know whether to trust.}

@@

\subsection{What is credible?}

\subsection{The distributional hypothesis}

\subsection{Contradiction Detection}

\subsection{Sentiment Analysis}

\subsection{Crowdsourcing disputed claims}

\x{Dispute Finder. Wikipedia. WikiTrust}

\subsection{Curated Databases of Disputed Claims}

\x{Dispute Finder.}

\section{Finding Disputed Claims}

\subsection{Disputed Templates}

\x{Include a table with templates we use and templates we generated}

\subsection{Selecting Good Statements}

\subsection{Generating New Templates}

\x{Following the distributional hypothesis.}
\x{Search for known disputed claims and find most frequent words that surround them.}

\section{Using Disputed Claims}

\x{We are building lots of applications that will use this data set.}
\x{Dispute Finder highlights disputed claims on the web.}
\x{Tell people when audio they hear is disputed.}
\x{Tell people when a source you trust disagrees with others.}
\x{Tell me when a source I read in the past is now disputed.}
\x{Tell me how contentious a topic is.}
\x{Let me explore what is disputed about a particular topic.}
\x{Tell me when something new is disputed about a topic I care about.}
\x{Examine the zeitgeist of disputes.}
\x{Tell me about things that are disputed by the kind of sites I trust.}
\x{We also want to make this data set available to others.}

\section{Analysing the Data}

\subsection{Data Quality}

\x{Look at a random sample of the data and say how clean it is.}
\x{Evaluate the quality of the claims that we extracted.}
\x{Evaluate the quality of the clusters that we created.}
\x{Evaluate the quality of the different individual templates - which ones have the highest quality claims.}

\subsection{Trends over time}

\x{Look at what noun phrases were most disputed at particular years.}
\x{Look at what noun phrases were most disputed on particular days.}

\section{Conclusions}

\x{We can use the web as a corpus to determine what people think is disputed.}
